Learning to Synthesize Rules for Network Intrusion Detectors

### 2020-03-03 paper/paper.tex
table RQ2

>>>>

\setlength{\tabcolsep}{3pt}
\begin{table}[h!]
  \small
  \caption{\label{table:results}Results.}
  \vspace{-2ex}
  \centering
  \begin{tabular}{lrrrrrr}
    \toprule
    Name &
    Opt weights &
    4.3.2 &
    4.3.3 &    
    4.3.4 &
    4.3.5 \\ 
    Black Nurse & 2 & 2 & 2 & 2 & 7 \\    
    Ping Scan & 2 & 2 & 2 & 2 & 8 \\
    SYN Flood & 2 & 2 & 2 & 2 & 2 \\
    UDP Teardrop & 4 & 4 & 4 & 4 & 4 \\
    %%UDP Flood & - & - & - & - & - \\

    %%Apache Struts 2 & - & - & - & - & - & -\\
    ColdFusion & 3 & 2 & 12 & 5 & 3 \\
    iisadmin access & 1 & 1 & 1 & 8 & 1 \\        
    JBoss JMX & 45 & 5 & 45 & 111 & 45 \\
    Script tag in URI & 1 & 4 & 1 & 8 & 1 \\
    WeBid LFI & 10 & 77 & 28 & 32 & 10 \\    
    %%Wordpress Login & 8 & - & - & - & - \\
    .htaccess access & 2 & 2 & 2 & 17 & 2 \\
    .idq access & 2 & 2 & 2 & 12 & 2 \\
    /system32/ in URI & 4 & 20 & 1 & 58 & 4 \\
    Basebuilder LFI & 34 & 117 & 57 & 183 & 34 \\
    Tomcat Snoop Access & 32 & 828 & 2 & 2564 & 32 \\
    \bottomrule
  \end{tabular}
\end{table}
